method

### 2022-02-22 06_Paper/ER-ED/method.Rmd
cross referenced supplement
corrected typo

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ... +3), the reliability of the measures. -->

>>>>

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires). <!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ... +3), the reliability of the measures. -->
